### 2015-06-04 doc/manual/overview.tex
Added hyperlinks to manual

@@

\section{Geometry options}
In \sfincs, a variety of options are available for the magnetic field geometry.  The geometry can be read directly
from a {\ttfamily vmec wout}
file, or from the {\ttfamily .bc} format Boozer-coordinate data files used at the Max Planck Institute for Plasma Physics (IPP).
A general analytic model for the magnetic field is also available, given by equation (\ref{eq:Bmodel}),
as are several analytic models for LHD and W7-X in which 3 or 4 Fourier components are retained.
The primary switch for controlling the magnetic geometry in \sfincs~is the {\ttfamily geometryScheme} parameter
in the {\ttfamily geometryParameters} input namelist.
For more details about geometry options in \sfincs, see section \ref{sec:geometryParameters}.

@@

%\begin{figure}[htbp]
%\begin{center}
%%\includegraphics[width=1.0\textwidth]{poloidal_cross-sections.pdf}
%\mycaption{Trajectories of trapped particles.  (a) In tokamaks and omnigenous stellarators,
%all collisionless trajectories are confined.  (b) In contrast, trapped particles in other stellarators
%may have a radial drift that does not average to zero.
%\label{fig:poloidal_cross_sections}}
%\end{center}
%\end{figure}

>>>>

\item
The electrostatic potential can either be taken to be constant or non-constant on a flux surface.

@@

\section{Geometry options}
In \sfincs, a variety of options are available for the magnetic field geometry.  The geometry can be read directly
from a {\ttfamily vmec wout}
file, or from the {\ttfamily .bc} format Boozer-coordinate data files used at the Max Planck Institute for Plasma Physics (IPP).
A general analytic model for the magnetic field is also available, given by equation (\ref{eq:Bmodel}),
as are several analytic models for LHD and W7-X in which 3 or 4 Fourier components are retained.
The primary switch for controlling the magnetic geometry in \sfincs~is the \parlink{geometryScheme} parameter
in the {\ttfamily \hyperref[sec:geometryParameters]{geometryParameters}} input namelist.
For more details about geometry options in \sfincs, see section \ref{sec:geometryParameters}.

@@

### 2015-06-04 doc/manual/resolution.tex
Added to user manual
Added hyperlinks to manual

Results from \sfincs~should only be believed if you are confident they
are converged with respect to the numerical resolution parameters
\Ntheta, \Nzeta, \Nxi, and \Nx.  That is, you want to be sure the
physics output of the code does not change significantly when any of
these parameters are increased. The values of \Ntheta, \Nzeta, \Nxi,
and \Nx~required for convergence depend strongly on the magnetic
geometry and collisionality, with modest dependence also on the radial
electric field. It is strongly recommended that you test for
convergence with respect to \Ntheta, \Nzeta, \Nxi, and \Nx~whenever
beginning \sfincs~calculations for a new scenario.

@@

There are several resolution parameters which are almost never the limiting factor
for convergence, and so which almost never need to be adjusted.
These parameters and good values for them are {\ttfamily NL=4}, 
{\ttfamily solverTolerance} = $10^{-6}$,
{\ttfamily xMax=5.0},
and {\ttfamily NxPotentialsPerVth=40.0}.  The latter two of these parameters are in fact ignored
for the recommended and default {\ttfamily xGridMode} setting, 5.

@@

When the mean-free-path is shorter than the parallel length scale of the equilibrium,
({\ttfamily nuPrime} $\ge$ 1), the parameters required for convergence
do not depend much on collisionality. In the opposite
limit in which the mean-free-path is longer than the parallel length scale of the equilibrium,
({\ttfamily nuPrime} $\le$ 1)
values of
\Nzeta~and \Nxi~required for convergence increase dramatically
as collisionality decreases. The required value of \Ntheta~increases as well, but often
not quite as dramatically. The \Nx~required for convergence does not depend
much on collisionality, though typically the required value increases
slightly with collisionality at high collisionality

The \Nx~required for convergence may need to increase slightly with the number of species.
Typically you can expect to use \Nx=5-8.

@@

>>>>

Results from \sfincs~should only be believed if you are confident they
are converged with respect to the numerical resolution parameters
\Ntheta, \Nzeta, \Nxi, and \Nx.  That is, you want to be sure the
physics output of the code does not change significantly when any of
these parameters are increased. The values of \Ntheta, \Nzeta, \Nxi,
and \Nx~required for convergence depend strongly on the magnetic
geometry and collisionality. It is strongly recommended that you test for
convergence with respect to \Ntheta, \Nzeta, \Nxi, and \Nx~whenever
beginning \sfincs~calculations for a new scenario.

@@

There are several resolution parameters which are almost never the limiting factor
for convergence, and so which almost never need to be adjusted.
These parameters and good values for them are \NL = 4, 
\parlink{solverTolerance} = $10^{-6}$,
\parlink{xMax} = 5.0,
and \parlink{NxPotentialsPerVth} = 40.0.  
(These values are set as the defaults.)
The latter two of these parameters are in fact ignored
for the recommended and default \parlink{xGridScheme} setting, 5.

@@

When the mean-free-path is shorter than the parallel length scale of the equilibrium,
%({\ttfamily nuPrime} $\ge$ 1), 
the parameters required for convergence
do not depend much on collisionality. In the opposite
limit in which the mean-free-path is longer than the parallel length scale of the equilibrium,
%({\ttfamily nuPrime} $\le$ 1)
values of
\Nzeta~and \Nxi~required for convergence increase dramatically
as collisionality decreases. The required value of \Ntheta~increases as well, but often
not quite as dramatically. The \Nx~required for convergence does not depend
nearly as much on collisionality.  The reason is that
at low collisionality, a boundary layer develops in the distribution function
along the boundary between trapped and passing (untrapped) particles.
The location of this boundary depends on $\theta$, $\zeta$, and $\xi$,
and so high resolution is required in these coordinates to resolve the boundary layer.
But the location of the trapped-passing boundary is independent
of $x$, and hence the resolution requried in $x$ is not particularly high.

Typically you can expect to use \Nx = 5-8, with 5 being sufficient at low collisionality
and 8 being required at high collisionality.
The \Nx~required for convergence may need to increase slightly with the number of species.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\textwidth]{sfincsConvergenceScan.pdf}
\mycaption{Plot generated by \sfincsScanPlot showing a resolution convergence scan for the example
{\ttfamily geometryScheme4\_2species\_noEr}.
\label{fig:convergence}}
\end{center}
\end{figure}

To check how well the results of \sfincs~are converged with respect to the resolution
parameters, run \sfincsScan~with \parlink{scanType} = 1.
In this type of scan, a ``base case'' is first run at the
values of \Ntheta, \Nzeta, \Nxi, and \Nx~specified in the input file.
Then, each of these parameters will be varied in turn, holding the other parameters fixed.
The range of \Ntheta~in the scan is specified by the parameters \parlink{NthetaMinFactor},
\parlink{NthetaMaxFactor}, and \parlink{NthetaNumRuns}. 
Each of these three parameters is read by \sfincsScan~rather than by \sfincs~itself,
and so it must be prefaced by {\ttfamily !ss} in the input namelist file.
The ranges of \Nzeta, \Nxi, and \Nx~are set by parameters with analogous names,
as detailed in section \ref{sec:scanType1Parameters}.

For example, suppose you initially run \sfincsScan~with \Ntheta = 15, 
\parlink{NthetaMinFactor} = 0.7, \parlink{NthetaMaxFactor} = 1.5, and 
\parlink{NthetaNumRuns} = 5.
This will generate \sfincs~runs at \Ntheta = 11, 13, 15 (the base case), 19, and 23.
Notice that \sfincsScan~automatically ensures that only odd values are used.
(Only odd values of \Ntheta~and \Nzeta~are used internally in \sfincs.)
The maximum and minimum values for the scan, 11 and 23, are the nearest odd integers
to \Ntheta$\times$\parlink{NthetaMinFactor} and \Ntheta$\times$\parlink{NthetaMaxFactor} respectively.
Notice also that there are `gaps' at  \Ntheta = 17 and 21 since \sfincsScan~attempts to space the values
logarithmically rather than uniformly.

In addition to the 4 resolution parameters above, \sfincsScan~also allows the parameters
\parlink{solverTolerance}, \parlink{xMax}, and \parlink{NxPotentialsPerVth}
to be scanned.  These latter two parameters are not used for the default \parlink{xGridScheme}
so it is usually unnecessary to scan them.  It is also usually unnecessary to scan \parlink{solverTolerance}
since the default value is usually robust.

A directory will be created for each run.  Each directory will contain
a copy of {\ttfamily input.namelist} in which \Ntheta, \Nzeta, \Nx, or \Nxi~has been
altered appropriately by \sfincsScan. Each directory will also contain a job file for the run.

You do not need to scan all variables. For example, if you do not wish to scan \Nx,
you can either set \parlink{NxNumRuns} = 0, or you can not specify
\parlink{NxNumRuns} in the {\ttfamily input.namelist} file.

Once the individual runs in the scan have begun to finish, you can plot the results by running \sfincsScanPlot.
You can plot the results before all the runs in the scan finish, although at least the base case
run must be completed.  Different quantities will be displayed depending on
\parlink{RHSMode} and \parlink{includePhi1}.

Typical convergence behavior is illustrated in figure \ref{fig:convergence},
showing the results of \sfincsScan~and \sfincsScanPlot~for the example
{\ttfamily geometryScheme4\_2species\_noEr}.
In this figure, a very large number of values are included for the resolution
parameters, more than you would likely include in routine use of the code.
The red vertical lines emphasize the ``base case'' resolution parameters.
For all parameters scanned, the physical output quantities (particle flux, heat flux, etc)
are essentially unchanged when any of the resolution parameters
are increased beyond the base case value.  Thus, the results in the base case are converged,
and so we can believe the results.
Observe in the figure that the output quantities tend to oscillate when \Nxi~is incremented by 1 and insufficient
\Nxi~is used. Results for even and odd \Nxi~converge to the same value, as one would hope.

If you wish to add more runs to the scan at a later time,
you can alter the relevant \sfincsScan~parameters in the original {\ttfamily input.namelist}~file
and run \sfincsScan~again from the original directory.  The \sfincsScan~code will automatically detect which runs
have already been submitted, so duplicate runs will not be generated.
For example, consider the scan of \Ntheta~described previously in this section,
and suppose you wish to fill in the gaps at \Ntheta = 17 and 21 in the original scan.
To do this, you could set \parlink{NthetaNumRuns} to a large number like 100
and re-run \sfincsScan.  Since \sfincsScan~intelligently avoids duplication,
the only new runs generated will be  \Ntheta = 17 and 21.

If you are ultimately intending to scan $E_r$, you probably only need to run a convergence scan
at a single value of $E_r$.  This is because the resolution requirements of \sfincs~are not sensitive to
$E_r$, as discussed above.
Also, if you are ultimately intending to run \sfincs~at a range of minor radii,
it is reasonably to only run a convergence scan at a single radius close to the magnetic axis.
This is because the typically peaked shape of the temperature profile means that
collisionality is lowest near the axis.  Since the resolution requirements of \sfincs~are most
demanding at low collisionality, then if the code is converged at the radius of lowest collisionality,
it should be converged at all radii.

### 2015-06-04 doc/manual/runs.tex
Example input files pared down to non-default parameters, since documentation is now in user manual.
Added hyperlinks to manual

You can choose any reference parameters you like, not just the values
suggested here. However, if you use a {\ttfamily vmec} or {\ttfamily .bc} magnetic equilibrium
by choosing {\ttfamily geometryScheme} = 5, 11, or 12, then you MUST use $\bar{B}$ = 1 Tesla and $\bar{R}$ = 1 meter.
The code ``knows'' about the reference values only through
the 3 combinations {\ttfamily Delta}, {\ttfamily alpha}, and {\ttfamily nu\_n}
in the {\ttfamily physicsParameters} namelist.

@@

{\ttfamily psiHat} = $\hat\psi$ is the toroidal flux (divided by $2\pi$), normalized by $\bar{B}\bar{R}^2$.\\

{\ttfamily psiN} = $\psi_N$ is the toroidal flux normalized by its value at the last closed flux surface.\\

{\ttfamily rHat} = $\hat{r}$ is defined as {\ttfamily aHat}$\sqrt{\mbox{\ttfamily psiN}}$, where {\ttfamily aHat} is an effective minor radius of the last closed flux surface normalized by $\bar{R}$.\\

{\ttfamily rN} = $r_N$ is defined as $\sqrt{\mbox{\ttfamily psiN}}$.\\

@@

When setting up a run, you can make several independent choices for radial coordinates.  One parameter
you select is {\ttfamily inputRadialCoordinateForGradients} in the {\ttfamily geometryParameters} namelist.
This parameter controls which coordinate is used to specify the gradients. The possible values of {\ttfamily inputRadialCoordinateForGradients} are:\\

@@

0: Use derivatives with respect to {\ttfamily psiHat}: Density gradients are specified using {\ttfamily dnHatdpsiHats}, 
temperature gradients are specified using {\ttfamily dTHatdpsiHats},  a single $E_r$ is specified using
{\ttfamily dPhiHatdpsiHat}, and a range of $E_r$ for a scan is specified using {\ttfamily dPhiHatdpsiHatMin}-{\ttfamily dPhiHatdpsiHatMax}.
\\

1: Use derivatives with respect to {\ttfamily psiN}: Density gradients are specified using {\ttfamily dnHatdpsiNs}, 
temperature gradients are specified using {\ttfamily dTHatdpsiNs},  a single $E_r$ is specified using
{\ttfamily dPhiHatdpsiN}, and a range of $E_r$ for a scan is specified using {\ttfamily dPhiHatdpsiNMin}-{\ttfamily dPhiHatdpsiNMax}.
\\

2: Use derivatives with respect to {\ttfamily rHat}: Density gradients are specified using {\ttfamily dnHatdrHats}, 
temperature gradients are specified using {\ttfamily dTHatdrHats},  a single $E_r$ is specified using
{\ttfamily dPhiHatdrHat}, and a range of $E_r$ for a scan is specified using {\ttfamily dPhiHatdrHatMin}-{\ttfamily dPhiHatdrHatMax}.
\\

3: Use derivatives with respect to {\ttfamily rN}: Density gradients are specified using {\ttfamily dnHatdrNs}, 
temperature gradients are specified using {\ttfamily dTHatdrNs},  a single $E_r$ is specified using
{\ttfamily dPhiHatdrN}, and a range of $E_r$ for a scan is specified using {\ttfamily dPhiHatdrNMin}-{\ttfamily dPhiHatdrNMax}.
\\

@@

Another choice involving radial coordinates is how to specify the flux surface for the computation.
This choice is made using the parameter {\ttfamily inputRadialCoordinate} in the {\ttfamily geometryParameters}
namelist, which is again an integer from 0 to 3, and this parameter need not be the same as {\ttfamily inputRadialCoordinateForGradients}.
An extra complication with specifying the flux surface is that the magnetic equilibrium file will contain data on a finite number of surfaces,
and you may wish to use one of these surfaces.  For this reason, the parameters for specifying the flux surface have {\ttfamily \_wish}
appended to the name. In other words, the allowed values for {\ttfamily inputRadialCoordinate} are:\\

@@

0: Specify the flux surface using {\ttfamily psiHat\_wish}.\\

1: Specify the flux surface using {\ttfamily psiN\_wish}.\\

2: Specify the flux surface using {\ttfamily rHat\_wish}.\\

3: Specify the flux surface using {\ttfamily rN\_wish}.\\

@@

When using {\ttfamily geometryScheme} == 11 or 12, \sfincs~will always shift the ``wish'' value so it matches an available surface in the magnetic equilibrium file.
For {\ttfamily geometryScheme} == 5, the {\ttfamily VMECRadialOption} parameter lets you can choose whether to shift to the nearest surface in the magnetic equilibrium file,
or to interpolate the \vmec~data onto the exact value of radius you specify.

If you perform a radial scan, then there is a third choice you can make: which radial coordinate to use in the {\ttfamily profiles} file.
This choice is made with an integer 0, 1, 2, or 3 in the first non-comment line of the {\ttfamily profiles} file.
The radial coordinate used in the {\ttfamily profiles} file need not be the same as either
{\ttfamily inputRadialCoordinate} or {\ttfamily inputRadialCoordinateForGradients}.
Note however that the maximum and minimum radial electric field specified in the {\ttfamily profiles}
file must be defined as the derivative of the electrostatic potential with respect to the radial coordinate {\ttfamily inputRadialCoordinateForGradients}.

For more details about the behavior of {\ttfamily inputRadialCoordinate}, {\ttfamily inputRadialCoordinateForGradients}, and {\ttfamily VMECRadialOption},
see section \ref{sec:geometryParameters}.

@@

As discussed in \cite{sfincsPaper},
one of the capabilities of \sfincs~is to compare various models for the terms in the kinetic equation involving $E_r$.
These variations of the kinetic equation are called ``trajectory models'' in \cite{sfincsPaper}.
The relevant terms in the kinetic equation can be turned off and on by certain Boolean parameters in the {\ttfamily physicsParameters} namelist.
The models described in \cite{sfincsPaper} are selected as follows:\\

@@

\underline{Full trajectories:}\\
{\ttfamily 
includeXDotTerm = .true.\\
includeElectricFieldTermInXiDot = .true.\\
useDKESExBDrift = .false.\\
}

\underline{Partial trajectories:}\\
{\ttfamily
includeXDotTerm = .false.\\
includeElectricFieldTermInXiDot = .false.\\
useDKESExBDrift = .false.\\
}

\underline{DKES trajectories:}\\
{\ttfamily
includeXDotTerm = .false.\\
includeElectricFieldTermInXiDot = .false.\\
useDKESExBDrift = .true.\\
}
}

@@

In \sfincs, you can choose whether or not to
include $\Phi_1$ using the paramter {\ttfamily includePhi1} in the {\ttfamily physicsParameters}
namelist.  If and only if $\Phi_1$ is included, a quasineutrality equation is solved
at each point on the flux surface.  Due to these extra unknowns ($\Phi_1$) and extra equations
(quasineutrality), the system matrix is slightly larger when {\ttfamily includePhi1} is \true.
Specifically, the number of rows and columns are each increased by \Ntheta$\times$\Nzeta$+1$.  This increase is miniscule compared
to the number of rows and columns associated with the kinetic equation, which depends not only on real space
but also on velocity space and species.  Thus, there is very little extra computational cost associated
with {\ttfamily includePhi1}.  You may wish to set {\ttfamily includePhi1} = \true~when
using \sfincs~to model an experiment, and set  {\ttfamily includePhi1} = \false~when
comparing \sfincs~with analytic theory or with another code that does not include $\Phi_1$.

@@

By setting {\ttfamily RHSMode=3}, \sfincs~can be run in a mode
where it solves the same kinetic equation (prior to discretization) as {\ttfamily dkes}
and other monoenergetic codes.
When {\ttfamily RHSMode=3}, the values of {\ttfamily Zs}, {\ttfamily THats}, {\ttfamily nHats},
{\ttfamily mHats}, {\ttfamily nu\_n}, and {\ttfamily dPhiHatdXXX} are all ignored.
Instead, the collisionality is set by {\ttfamily nuPrime}, and the radial electric field is set
by {\ttfamily EStar}.  The first of these quantities is the dimensionless collisionality
\begin{equation}
\mbox{\ttfamily nuPrime} = \frac{(G+\iota I) \nu}{v B_0}
\end{equation}
where $G$ and $I$ are defined in (\ref{eq:covariant}), $\iota=1/q$ is the rotational transform,
$v$ is the speed at which the monoenergetic calculation is being performed, and $B_0$ is the (0,0) Fourier harmonic of $B$
with respect to the Boozer poloidal and toroidal angles. The collision
frequency $\nu$ is here the value of $\nu_\mathrm{ii}$ one would have if
$v$ were the thermal speed. That is, in SI units,
\begin{equation}
  \nu=\frac{4}{3\sqrt{\pi}}\frac{n Z^4e^4\ln \Lambda}{4\pi\epsilon_0^2m^2v^3}.
\end{equation}
%
The normalized radial electric field is
\begin{equation}
\mbox{\ttfamily EStar} = \frac{cG}{\iota v B_0} \frac{d\Phi}{d\psi}
\end{equation}
(Gaussian units).
When {\ttfamily RHSMode} == 1, {\ttfamily nuPrime} and {\ttfamily EStar} are ignored.
\todo{Should be change the behavior of RHSMode=2 so it uses nuPrime and EStar instead of nu\_n?}

The two parameters {\ttfamily nuPrime} and {\ttfamily EStar} are
related to the corresponding DKES parameters {\ttfamily CMUL} and
{\ttfamily EFIELD} by
\begin{eqnarray}
  \mbox{\ttfamily
    CMUL}&\equiv&\frac{\nu_\mathrm{D}}{v}=\frac{3\sqrt{\pi}}{4}\left(\mathrm{erf}(1)-\mathrm{Ch}(1)\right)
  \frac{B_0}{G+\iota I}\mbox{\ttfamily nuPrime},\\
  \mbox{\ttfamily EFIELD}&\equiv&-\left[\frac{d\Phi}{dr}\right]_\mathrm{DKES}\frac{1}{vB_0}=-\frac{\iota}{G}\left[\frac{d\Psi}{dr}\right]_\mathrm{DKES}\mbox{\ttfamily EStar},
\end{eqnarray}
where $\mathrm{Ch}$ is the Chandrasekhar function and $\nu_\mathrm{D}$
is the actual pitch-angle deflection frequency of the particle.
\todo{These expressions are in SI units. Should there be some
  factors of $c$ to adhere to the Gaussian standard used here?
  Probably not.}

>>>>

You can choose any reference parameters you like, not just the values
suggested here. However, if you use a {\ttfamily vmec} or {\ttfamily .bc} magnetic equilibrium
by choosing \parlink{geometryScheme} = 5, 11, or 12, then you MUST use $\bar{B}$ = 1 Tesla and $\bar{R}$ = 1 meter.
The code ``knows'' about the reference values only through
the 3 combinations \parlink{Delta}, \parlink{alpha}, and \parlink{nu\_n}
in the {\ttfamily \hyperref[sec:physicsParameters]{physicsParameters}} namelist.

@@

{\ttfamily \hypertarget{psiHat}{psiHat}} = $\hat\psi$ is the toroidal flux (divided by $2\pi$), normalized by $\bar{B}\bar{R}^2$.\\

{\ttfamily \hypertarget{psiN}{psiN}} = $\psi_N$ is the toroidal flux normalized by its value at the last closed flux surface.\\

{\ttfamily \hypertarget{rHat}{rHat}} = $\hat{r}$ is defined as {\ttfamily aHat}$\sqrt{\mbox{\ttfamily psiN}}$, where {\ttfamily aHat} is an effective minor radius of the last closed flux surface normalized by $\bar{R}$.\\

{\ttfamily \hypertarget{rN}{rN}} = $r_N$ is defined as $\sqrt{\mbox{\ttfamily psiN}}$.\\

@@

When setting up a run, you can make several independent choices for radial coordinates.  One parameter
you select is \parlink{inputRadialCoordinateForGradients} in the 
{\ttfamily \hyperref[sec:geometryParameters]{geometryParameters}} namelist.
This parameter controls which coordinate is used to specify the gradients. The possible values of \parlink{inputRadialCoordinateForGradients} are:\\

@@

0: Use derivatives with respect to {\ttfamily psiHat}: Density gradients are specified using \parlink{dnHatdpsiHats}, 
temperature gradients are specified using \parlink{dTHatdpsiHats},  a single $E_r$ is specified using
\parlink{dPhiHatdpsiHat}, and a range of $E_r$ for a scan is specified using \parlink{dPhiHatdpsiHatMin}-\parlink{dPhiHatdpsiHatMax}.
\\

1: Use derivatives with respect to {\ttfamily psiN}: Density gradients are specified using \parlink{dnHatdpsiNs}, 
temperature gradients are specified using \parlink{dTHatdpsiNs},  a single $E_r$ is specified using
\parlink{dPhiHatdpsiN}, and a range of $E_r$ for a scan is specified using \parlink{dPhiHatdpsiNMin}-\parlink{dPhiHatdpsiNMax}.
\\

2: Use derivatives with respect to {\ttfamily rHat}: Density gradients are specified using \parlink{dnHatdrHats}, 
temperature gradients are specified using \parlink{dTHatdrHats},  a single $E_r$ is specified using
\parlink{dPhiHatdrHat}, and a range of $E_r$ for a scan is specified using \parlink{dPhiHatdrHatMin}-\parlink{dPhiHatdrHatMax}.
\\

3: Use derivatives with respect to {\ttfamily rN}: Density gradients are specified using \parlink{dnHatdrNs}, 
temperature gradients are specified using \parlink{dTHatdrNs},  a single $E_r$ is specified using
\parlink{dPhiHatdrN}, and a range of $E_r$ for a scan is specified using \parlink{dPhiHatdrNMin}-\parlink{dPhiHatdrNMax}.
\\

@@

Another choice involving radial coordinates is how to specify the flux surface for the computation.
This choice is made using the parameter \parlink{inputRadialCoordinate} in the {\ttfamily \hyperref[sec:geometryParameters]{geometryParameters}}
namelist, which is again an integer from 0 to 3, and this parameter need not be the same as \parlink{inputRadialCoordinateForGradients}.
An extra complication with specifying the flux surface is that the magnetic equilibrium file will contain data on a finite number of surfaces,
and you may wish to use one of these surfaces.  For this reason, the parameters for specifying the flux surface have {\ttfamily \_wish}
appended to the name. In other words, the allowed values for \parlink{inputRadialCoordinate} are:\\

@@

0: Specify the flux surface using \parlink{psiHat\_wish}.\\

1: Specify the flux surface using \parlink{psiN\_wish}.\\

2: Specify the flux surface using \parlink{rHat\_wish}.\\

3: Specify the flux surface using \parlink{rN\_wish}.\\

@@

When using \parlink{geometryScheme} == 11 or 12, \sfincs~will always shift the ``wish'' value so it matches an available surface in the magnetic equilibrium file.
For \parlink{geometryScheme} == 5, the \parlink{VMECRadialOption} parameter lets you can choose whether to shift to the nearest surface in the magnetic equilibrium file,
or to interpolate the \vmec~data onto the exact value of radius you specify.

If you perform a radial scan, then there is a third choice you can make: which radial coordinate to use in the {\ttfamily profiles} file.
This choice is made with an integer 0, 1, 2, or 3 in the first non-comment line of the {\ttfamily profiles} file.
The radial coordinate used in the {\ttfamily profiles} file need not be the same as either
\parlink{inputRadialCoordinate} or \parlink{inputRadialCoordinateForGradients}.
Note however that the maximum and minimum radial electric field specified in the {\ttfamily profiles}
file must be defined as the derivative of the electrostatic potential with respect to the radial coordinate \parlink{inputRadialCoordinateForGradients}.

For more details about the behavior of \parlink{inputRadialCoordinate}, \parlink{inputRadialCoordinateForGradients}, and \parlink{VMECRadialOption},
see section \ref{sec:geometryParameters}.

@@

As discussed in \cite{sfincsPaper},
one of the capabilities of \sfincs~is to compare various models for the terms in the kinetic equation involving $E_r$.
These variations of the kinetic equation are called ``trajectory models'' in \cite{sfincsPaper}.
The relevant terms in the kinetic equation can be turned off and on by certain Boolean parameters in the {\ttfamily \hyperref[sec:physicsParameters]{physicsParameters}} namelist.
The models described in \cite{sfincsPaper} are selected as follows:\\

@@

\underline{Full trajectories:}\\
{\ttfamily 
\parlink{includeXDotTerm} = .true.\\
\parlink{includeElectricFieldTermInXiDot} = .true.\\
\parlink{useDKESExBDrift} = .false.\\
}

\underline{Partial trajectories:}\\
{\ttfamily
\parlink{includeXDotTerm} = .false.\\
\parlink{includeElectricFieldTermInXiDot} = .false.\\
\parlink{useDKESExBDrift} = .false.\\
}

\underline{DKES trajectories:}\\
{\ttfamily
\parlink{includeXDotTerm} = .false.\\
\parlink{includeElectricFieldTermInXiDot} = .false.\\
\parlink{useDKESExBDrift} = .true.\\
}
}

@@

In \sfincs, you can choose whether or not to
include $\Phi_1$ using the paramter {\ttfamily \hyperlink{includePhi1}{includePhi1}} in the 
{\ttfamily \hyperref[sec:physicsParameters]{physicsParameters}}
namelist.  If and only if $\Phi_1$ is included, a quasineutrality equation is solved
at each point on the flux surface.  Due to these extra unknowns ($\Phi_1$) and extra equations
(quasineutrality), the system matrix is slightly larger when \parlink{includePhi1} is \true.
Specifically, the number of rows and columns are each increased by \Ntheta$\times$\Nzeta$+1$.  This increase is miniscule compared
to the number of rows and columns associated with the kinetic equation, which depends not only on real space
but also on velocity space and species.  Thus, there is very little extra computational cost associated
with \parlink{includePhi1}.  You may wish to set \parlink{includePhi1} = \true~when
using \sfincs~to model an experiment, and set \parlink{includePhi1} = \false~when
comparing \sfincs~with analytic theory or with another code that does not include $\Phi_1$.

@@

By setting \parlink{RHSMode} = 3, \sfincs~can be run in a mode
where it solves the same kinetic equation (prior to discretization) as 
\dkes~and other monoenergetic codes.
When \parlink{RHSMode} = 3, the values of \parlink{Zs}, \parlink{THats}, \parlink{nHats},
\parlink{mHats}, \parlink{nu\_n}, and {\ttfamily dPhiHatdXXX} are all ignored.
Instead, the collisionality is set by \parlink{nuPrime}, and the radial electric field is set
by \parlink{EStar}.  The first of these quantities is the dimensionless collisionality
\begin{equation}
\mbox{\parlink{nuPrime}} = \frac{(G+\iota I) \nu}{v B_0}
\end{equation}
where $G$ and $I$ are defined in (\ref{eq:covariant}), $\iota=1/q$ is the rotational transform,
$v$ is the speed at which the monoenergetic calculation is being performed, and $B_0$ is the (0,0) Fourier harmonic of $B$
with respect to the Boozer poloidal and toroidal angles. The collision
frequency $\nu$ is here the value of $\nu_\mathrm{ii}$ one would have if
$v$ were the thermal speed. That is, in SI units,
\begin{equation}
  \nu=\frac{4}{3\sqrt{\pi}}\frac{n Z^4e^4\ln \Lambda}{4\pi\epsilon_0^2m^2v^3}.
\end{equation}
%
The normalized radial electric field is
\begin{equation}
\mbox{\parlink{EStar}} = \frac{cG}{\iota v B_0} \frac{d\Phi}{d\psi}
\end{equation}
(Gaussian units).
When {\ttfamily RHSMode} == 1, {\ttfamily nuPrime} and {\ttfamily EStar} are ignored.
\todo{Should be change the behavior of RHSMode=2 so it uses nuPrime and EStar instead of nu\_n?}

The two parameters \parlink{nuPrime} and \parlink{EStar} are
related to the corresponding DKES parameters {\ttfamily CMUL} and
{\ttfamily EFIELD} by
\begin{eqnarray}
  \mbox{\ttfamily
    CMUL}&\equiv&\frac{\nu_\mathrm{D}}{v}=\frac{3\sqrt{\pi}}{4}\left(\mathrm{erf}(1)-\mathrm{Ch}(1)\right)
  \frac{B_0}{G+\iota I}\mbox{\ttfamily nuPrime},\\
  \mbox{\ttfamily EFIELD}&\equiv&-\left[\frac{d\Phi}{dr}\right]_\mathrm{DKES}\frac{1}{vB_0}=-\frac{\iota}{G}\left[\frac{d\Psi}{dr}\right]_\mathrm{DKES}\mbox{\ttfamily EStar},
\end{eqnarray}
where $\mathrm{Ch}$ is the Chandrasekhar function and $\nu_\mathrm{D}$
is the actual pitch-angle deflection frequency of the particle.
\todo{These expressions are in SI units. Should there be some
  factors of $c$ to adhere to the Gaussian standard used here?
  Probably not.}
